---
title: "20200910_SocialNetworkAnalysis"
author: "Jie Chen, Zach Friedman"
date: "9/10/2020"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


```{r, message = F, warning = F, results = "hide"}
# Load liraries and set working directory
library(tidyverse)
library(mstknnclust)
library(dplyr)
library(igraph)
library(reshape2)
library(stringr)
library(CINNA)
library(ggthemes)
library(linkcomm)
library(formattable)
```

```{r, results = "hide"}
#create list with file names
files <- list.files(path="C:/Users/Zachary Friedman/Desktop/ZColumbia/TLTL Research/aiedu/data/sna_tables", pattern="\\d.csv", full.names=TRUE, recursive=FALSE)

#start function which loops through files, creates graph objects, and summary metrics
lapply(files, function(x) {
year_name = paste(as.character(str_sub(x,nchar(x)-7, nchar(x)-6)),as.character(str_sub(x,nchar(x)-5, nchar(x)-4)),sep = "-")
Years = year_name

# Import data
sna_table <- read.csv(x)
rownames(sna_table) <- sna_table[,1]
sna_table <- sna_table[,-1]

assign(paste("sna_table",year_name,sep = ""),sna_table,envir = .GlobalEnv)

# Create adjacency list and graph
my_adj_list <- sna_table %>% as.matrix()

new_net <- graph_from_adjacency_matrix(my_adj_list, weighted= TRUE, mode = "undirected")

assign(paste("new_net",year_name,sep = ""),new_net,envir = .GlobalEnv)

# Graph Summary Measures
Edge_count = E(new_net) %>% length
Node_count = V(new_net) %>% length
Edge_density = edge_density(new_net) %>% round(3)
Diameter = diameter(new_net, directed = F)
Mean_distance = mean_distance(new_net) %>% round(3)
Top_pagerank = page.rank(new_net) %>% .[[1]] %>% sort %>% tail(1) %>% names


# Largest Connected Component Summary Measures

LCC = giant_component_extract(new_net, directed = FALSE)
LCC <- graph.data.frame(LCC[2])
LCC_edge_count = E(LCC) %>% length
New_net_edge_count = E(new_net) %>% length
LCC_frac_size = (LCC_edge_count/New_net_edge_count) %>% round(3)

LCC_edge_density = edge_density(LCC) %>% round(3)
LCC_diameter = diameter(LCC, directed = F)

LCC_top_eigencentrality = eigen_centrality(LCC) %>% .[[1]] %>% sort %>% tail(1) %>% names
LCC_mean_distance = mean_distance(LCC) %>% round(3)
LCC_top_pagerank = page.rank(LCC) %>% .[[1]] %>% sort %>% tail(1) %>% names

#Create table with summary measures and assign it to Global Environment so loop doesn't overwrite
table <- cbind(Years,Node_count, Edge_count, Edge_density,Diameter,Mean_distance,Top_pagerank,LCC_frac_size,LCC_edge_density) %>% tbl_df

assign(paste("table",year_name,sep = ""),table,envir = .GlobalEnv)

})
```

```{r,results = "hide"}
#Create lists of graph obects and tables for later uses in lapply functions
net_back_4 = as.list(paste("new_net",paste(as.character(str_sub(files,nchar(files)-7, nchar(files)-6)),as.character(str_sub(files,nchar(files)-5, nchar(files)-4)),sep = "-"),sep = ""))

net_list <- lapply(net_back_4, get)

sna_back_4 = as.list(paste("sna_table",paste(as.character(str_sub(files,nchar(files)-7, nchar(files)-6)),as.character(str_sub(files,nchar(files)-5, nchar(files)-4)),sep = "-"),sep = ""))

sna_list <- lapply(sna_back_4, get)

file_back_4 = as.list(paste("table",paste(as.character(str_sub(files,nchar(files)-7, nchar(files)-6)),as.character(str_sub(files,nchar(files)-5, nchar(files)-4)),sep = "-"),sep = ""))

table_list <- lapply(file_back_4, get)

table1 <- do.call(rbind,table_list)

```

## Network Metrics for Two Year Periods from 2013-2020 

```{r}
#Repeat the function two chunks above for all years

sna_all <- read.csv("data/sna_tables/sna_table.csv")
rownames(sna_all) <- sna_all[,1]
sna_all <- sna_all[,-1]


# Create adjacency list and graph
my_adj_list <- sna_all %>% as.matrix()

new_net <- graph_from_adjacency_matrix(my_adj_list, weighted= TRUE, mode = "undirected")

# Summary Measures
Edge_count = E(new_net) %>% length
Node_count = V(new_net) %>% length
Edge_density = edge_density(new_net) %>% round(3)
Diameter = diameter(new_net, directed = F)
Mean_distance = mean_distance(new_net) %>% round(3)
Top_pagerank = page.rank(new_net) %>% .[[1]] %>% sort %>% tail(1) %>% names

# Largest Connected Component Summary Measures

LCC = giant_component_extract(new_net, directed = FALSE)
LCC <- graph.data.frame(LCC[2])
LCC_edge_count = E(LCC) %>% length
New_net_edge_count = E(new_net) %>% length
LCC_frac_size = (LCC_edge_count/New_net_edge_count) %>% round(3)

LCC_edge_density = edge_density(LCC) %>% round(3)
LCC_diameter = diameter(LCC, directed = F)

LCC_top_eigencentrality = eigen_centrality(LCC) %>% .[[1]] %>% sort %>% tail(1) %>% names
LCC_mean_distance = mean_distance(LCC) %>% round(3)
LCC_top_pagerank = page.rank(LCC) %>% .[[1]] %>% sort %>% tail(1) %>% names
Years = "All Years"

table2 <- table1 %>% rbind(cbind(Years,Node_count, Edge_count, Edge_density,Diameter,Mean_distance,Top_pagerank,LCC_frac_size,LCC_edge_density)) %>% tbl_df

table2 %>% formattable()
```

## Network Metric Visualizations

```{r}
# Visualization/Analysis
final_table <- table2

par(mfrow=c(1,2))

final_table %>% filter(Years!= "All Years") %>% ggplot + geom_col(mapping = aes(x=Years, y = as.numeric(Edge_count)),fill = "royalblue1") + geom_label(aes(x=Years, y = as.numeric(Edge_count), label = as.numeric(Edge_count))) + theme_bw() + labs(x = "Network Time Period", y = "Graph Edge Count", title = "Connections Between Authors Over Time")


final_table %>% filter(Years!= "All Years") %>% ggplot + geom_col(mapping = aes(x =Years, y = as.numeric(Node_count)),fill = "red4") + geom_label(aes(x=Years, y = as.numeric(Node_count), label = as.numeric(Node_count))) + theme_bw() + labs(x = "Network Time Period", y = "Graph Node Count", title = "Number of Authors Publishing Over Time")

final_table %>% ggplot + geom_col(mapping = aes(x =Years, y = as.numeric(Edge_density)),fill = "forestgreen") + geom_label(aes(x=Years, y = as.numeric(Edge_density), label = as.numeric(Edge_density))) + theme_bw() + labs(x = "Network Time Period", y = "Edge Density", title = "Connectendess of Network Graph Over Time")

# final_table %>% ggplot + geom_col(mapping = aes(x =Years, y = as.numeric(Mean_distance)),fill = "slateblue") + geom_label(aes(x=Years, y = as.numeric(Mean_distance), label = as.numeric(Mean_distance))) + theme_bw() + labs(x = "Network Time Period", y = "Mean Distance Between Nodes", title = "Sparsity of Network Over Time")

final_table %>% ggplot + geom_col(mapping = aes(x =Years, y = as.numeric(LCC_frac_size)),fill = "sienna3") + geom_label(aes(x=Years, y = as.numeric(LCC_frac_size), label = as.numeric(LCC_frac_size))) + theme_bw() + labs(x = "Network Time Period", y = "LCC Fraction (LCC Edge Count/Network Edge Count)", title = "Size of Largest Connected Componenet as a Fraction of Whole Network")

```

### Findings

* 2017-2018 had the most connections, nearly two times as many as any other two year time period.

* 2013-2014 had the least authors publish of any two year time period. 2017-2018 had the most, as expected.

* 2013-2014 had the most connections per author, with 2019-2020 being close behind

* 2017-2018 had the largest single network as a proportion of its total network size.

## Community/Cluster Visualizations and Statistics 

```{r, cache = T, results = "hide"}
#Create lists of edges from graphs to use in getLinkCommunities function
edge_list_all <- lapply(net_list, as_edgelist)

lc <- lapply(edge_list_all, getLinkCommunities, hcmethod = "single")

lapply(lc, plot, type = "graph", layout = layout.fruchterman.reingold)

par(mfrow=c(1,2))
```

```{r}
#Show all information in Communities' objects
lc
```



```{r}
#Other Plotting Tests


# for (i in 1:length(net_list)) { plot(net_list[[i]],vertex.color="lightblue", vertex.size=5, vertex.label=NA) }
# par(mfrow=c(1,2))
# 
# lapply(net_list, plot, vertex.color="lightblue", vertex.size=5, vertex.label=NA)


# jpeg(filename='graph.jpg',width=2000,height=2000,units='px')
# plot(new_net, layout = layout.fruchterman.reingold, vertex.size=2, vertex.label=NA, edge.color=grey(0.85), edge.width = E(net)$weight)

```


```{r,results = "hide"}
#Other Clustering Tests

# Clustering mst.knn = 20 clusters
# lapply(files, function(x) {
# sna_table <- read.csv(x)
# rownames(sna_table) <- sna_table[,1]
# sna_table <- sna_table[,-1]
# year_name = paste(as.character(str_sub(x,nchar(x)-7, nchar(x)-6)),as.character(str_sub(x,nchar(x)-5, nchar(x)-4)),sep = "-")
# Create adjacency list 

# my_adj_list <- sna_table %>% as.matrix()

# clustering
# results <- mst.knn(my_adj_list)
# cluster_df <- results$partition
# cluster_df <- cluster_df %>% select(name = object, cluster = cluster)

#   
# assign(paste("author_clusters",year_name,sep = ""),cluster_df,envir = .GlobalEnv)
# })
```
